\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-07-29 NAR_DRAFT.tex
comments

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{\textbf{BATCAVE }}
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

\section{RESULTS}
% \begin{figure*}[t]
%   \begin{center}
%   \includegraphics{figures/aml_plot.pdf}
%   \end{center}
%   \caption{Model performance on 300X Whole leukemia genome.
%   \textbf{(a)} Precision/recall curves and \textbf{(c)} Reciever operating characteristic curves.
%   Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
%   A perfectly calibrated model would generate the diagonal line.}
%   \label{NAR-aml}
% \end{figure*}
\begin{figure*}
  \begin{center}
  \includegraphics{figures/fig2.pdf}
  \end{center}
  \caption{Model performance on 500X simulated whole exome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.}
\label{NAR-wes_fig}
\end{figure*}

@@

We measured calibration performance using the Integrated Calibration Index described in Methods \citep{Austin2019}.

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\textwidth}{@{}lllllllll@{}}
\toprule
Depth & Signature & $\mu$ & AUROC &  & AUPRC & & ICI & 
\\
& & (estimated) & MuTect & Calibrated & MuTect & Calibrated & MuTect & Calibrated
\\
\colrule
100X whole genome & Concentrated & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Intermediate & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Diffuse & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
500X whole exome & Concentrated & Row 1 & .848 & .928 & .674 & .757 & .0585 & .0465
\\
500X whole exome & Intermediate & Row 1 & .847 & .842 & .677 & .707 & .0587 & .0566 
\\
500X whole exome & Diffuse & Row 1 & .850 & .873 & .676 & .698 & .0565 & .0575
\\
AML 31 & Actual & $3.6e-8$ & .935 & .949 & .995 & .996 & 0.121 & 0.155
\\
\botrule
\end{tabular*}%
}
{$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
\end{table*}

>>>>

\usepackage{NAR-natbib}
\bibliographystyle{unsrtnat}
\usepackage{color}
\usepackage{xfrac}
\newcommand{\rngcomment}[1]{{\color{red}RNG: #1}}
\newcommand{\bkmcomment}[1]{{\color{blue}BKM: #1}}
\newcommand{\batcave}{BATCAVE }
% Enter dates of publication
\copyrightyear{2008}
\pubdate{31 July 2009}
\pubyear{2009}
\jvolume{37}
\jissue{12}

@@

\section{RESULTS}
% \begin{figure*}[t]
%   \begin{center}
%   \includegraphics{figures/aml_plot.pdf}
%   \end{center}
%   \caption{Model performance on 300X Whole leukemia genome.
%   \textbf{(a)} Precision/recall curves and \textbf{(c)} Reciever operating characteristic curves.
%   Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
%   A perfectly calibrated model would generate the diagonal line.}
%   \label{NAR-aml}
% \end{figure*}
\begin{figure*}
  \begin{center}
  \includegraphics{figures/fig2.pdf}
  \end{center}
  \caption{Model performance on 500X simulated whole exome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.\bkmcomment{change the axis on b and d to be the same as the steyerberg paper. much clearer}}
\label{NAR-wes_fig}
\end{figure*}

@@

We measured calibration performance using the Integrated Calibration Index described in Methods \citep{Austin2019}.
For all simulated tumors the calibration of \batcave is better across the full spectrum of posterior probabilities.
As we can see in Figure \ref{NAR-wes_fig} \textbf{b)} and \textbf{d)}, \batcave tends to increase posterior probabilities of low probability but true variants (top density curves), and decrease the probability of low probability but false variants (bottom density curves.).
As with all other metrics, the benefit of \batcave increases as the concentration of the mutation profile increases, and as sequencing depth increases.

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with $\mu$, auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\textwidth}{@{}lllllllll@{}}
\toprule
Depth & Signature & $\mu/\beta$ & AUROC &  & AUPRC & & ICI & 
\\
& & (estimated) & MuTect & \batcave & MuTect & \batcave & MuTect & \batcave
\\
\colrule
100X whole genome & Concentrated & 3.6e-7 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Intermediate & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
100X whole genome & Diffuse & Row 1 & Row 1 & -- & -- & -- & -- & --
\\
500X whole exome & Concentrated & Row 1 & .848 & .928 & .674 & .757 & .0585 & .0465
\\
500X whole exome & Intermediate & Row 1 & .847 & .842 & .677 & .707 & .0587 & .0566 
\\
500X whole exome & Diffuse & Row 1 & .850 & .873 & .676 & .698 & .0565 & .0575
\\
AML 31 & Actual & 3.6e-8 & .935 & .949 & .995 & .996 & 0.121 & 0.155
\\
\botrule
\end{tabular*}%
}
{$\mu$ = per-base mutation rate, AUROC/AUPRC = area under ROC/PRC curve, ICI = Integrated calibration index.}
\end{table*}
